Minimizing post shock forecasting error using disparate information

### 2020-06-07 manuscript/manuscript.tex
some edit at the end of introduction

Data integration for forecasting is a broad area of research including ideas from many areas. \citet{lee2020estimation} constructed a Bayesian hierarchical model embracing data integration %estimate posterior parameters for Richards model 
to improve predictive precision of COVID-19 infection trajectories for different countries. A similar setup may be beneficial for post-shock prediction but may be too dependent upon model specification for the shock distribution.
%, and conditions for predictive improvement are generally hard to know. 
\citet{plessen2020integrated} employed a data-mining approach to combine COVID-19 data from different countries as input to predict global net daily infections and deaths of COVID-19 using clustering. However, there is a tremendous amount of volatility in this form of COVID-19 data, and the fit of this prediction method may be improved with modeling structure or preprocessing of the donor pool. From a machine learning perspective, \citet{agarwal2020two} proposed a model-free synthetic intervention  method to predict unobserved potential outcomes after different interventions given a donor pool of observed outcomes with given interventions. Among those methodologies, they share the implicit assumption that candidates  from donor pool should be similar. In other words, caution should be dedicated to the construction of donor pool; otherwise, the result will be expected not to be  robust to the noise introduced by the insimilar ones. \emph{\textcolor{red}{More to be added ...}}

@@

\textbf{Need more of a transition to what we do here and why it is good.}
We develop and compare aggregation techniques in this post-shock setting and investigate settings for when they do and do not decrease mean squared prediction error. We assume a simple auto regressive data generating process similar to that in \citet{blundell1998initial} with a general random effects structure. The main idea is to first average the estimated shock effects from the disparate time series and then add the averaged estimated shock effect to the present forecast. When these time series are independent and the mean of shock effect distribution is large relative to its variance then this technique will reduce mean squared prediction error under the assumed model. Note that this methodology is not motivated with the goal of unbiased, asymptotically unbiased, or consistent estimation for the shock-effect of the time series under study. We consider three aggregation techniques: simple averaging, inverse-variance weighted averaging, and similarity weighting. The latter technique is similar to the weighting in synthetic control methodology \citep{abadie2010synthetic}.

\vspace*{0.25cm}\textbf{Need to discuss our example and our simulation results.}

@@

>>>>

Data integration for forecasting is a broad area of research including ideas from many areas. \citet{lee2020estimation} constructed a Bayesian hierarchical model embracing data integration %estimate posterior parameters for Richards model 
to improve predictive precision of COVID-19 infection trajectories for different countries. A similar setup may be beneficial for post-shock prediction but may be too dependent upon model specification for the shock distribution.
%, and conditions for predictive improvement are generally hard to know. 
\citet{plessen2020integrated} employed a data-mining approach to combine COVID-19 data from different countries as input to predict global net daily infections and deaths of COVID-19 using clustering. However, there is a tremendous amount of volatility in this form of COVID-19 data, and the fit of this prediction method may be improved with modeling structure or preprocessing of the donor pool. From a machine learning perspective, \citet{agarwal2020two} proposed a model-free synthetic intervention  method to predict unobserved potential outcomes after different interventions given a donor pool of observed outcomes with given interventions.

@@

Up to the scale of the shock, it is very unlikely that the above mentioned  statistical models or machine learning methods will work ideally since they are trained on the time series data that do not experience such a shock. To combat this problem, we develop and compare aggregation techniques in this post-shock setting based on the idea of data integration. We assume a simple auto regressive data generating process similar to that in \citet{blundell1998initial} with a general random effects structure. The main idea is to provide a scalar adjustment, based on estimated shock effects from the disparate time series, to the original forecast at the known shock time point.

We consider three aggregation techniques: simple averaging, inverse-variance weighted averaging, and similarity weighting. The latter technique is similar to the weighting in synthetic control methodology \citep{abadie2010synthetic}. We provide conditions  when the adjusted forecasts will work better than the original one, and estimate risk-reduction quantities to find the best technique out of the three. The involved parameters in the conditions and risk-reduction quantities are estimated by parametric bootstrap. Our simulation results show that  bootstrap estimation and the risk-reduction conditions are highly consistent with the truth when the model for the shock effects is identified well with appropriate covariates under a fixed design; and gain more precision when the donor pool size increases. In the real data example of forecasting stock price of Conoco Phillips that experienced a shock on 2020-03-09, the proposed three aggregation techniques work decently well. We now motivate our aggregation techniques.

% Note that this methodology is not motivated with the goal of unbiased, asymptotically unbiased, or consistent estimation for the shock-effect of the time series under study.

@@

For the use of our methodologies, caution should be dedicated to the construction of donor pool. Otherwise, the result will not be robust to the noises introduced by the unsimilar ones.
